Reaction-diffusion spatial modeling of COVID-19 in Chicago

### 2021-10-27 update-10-22/update-10-22.tex
plot updates
Fixed missing AR equation

%imports
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{footnote}
\usepackage{url}
\usepackage{natbib}

@@

@@

	\begin{align}
		S_t &=	\D_S \Delta S - \beta_{SA} S A - \beta_{SI} S I - \mu S, \\
		E_t	&=	\D_E \Delta E + \beta_{SA} S A + \beta_{SI} S I - (\sigma_A + \sigma_I) E, \\
		A_t	&=	\D_A \Delta A + \sigma_A E - M_{AR} A, \\
		I_t	&=	\sigma_I E - M I, \\
		H_t	&=	\gamma M I - (1 - \omega) \chi H - \omega \chi H, \\
		R_t	&=	(1 - \gamma) M I + (1 - \omega) \chi H, \\
		D_t	&=	\omega \chi H.
	\end{align}

>>>>

%imports
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{footnote}
\usepackage{url}
\usepackage{natbib}
\usepackage{pgfplots}

@@

	\begin{figure}[h]
		\centering
		\input{chicago-data}
		\label{fig:data}
		\caption{no}
	\end{figure}

@@

	\begin{align}
		S_t &=	\D_S \Delta S - \beta_{SA} S A - \beta_{SI} S I - \mu S, \\
		E_t	&=	\D_E \Delta E + \beta_{SA} S A + \beta_{SI} S I - (\sigma_A + \sigma_I) E, \\
		AR_t &= M_{AR} A, \\
		A_t	&=	\D_A \Delta A + \sigma_A E - M_{AR} A, \\
		I_t	&=	\sigma_I E - M I, \\
		H_t	&=	\gamma M I - (1 - \omega) \chi H - \omega \psi H, \\
		R_t	&=	(1 - \gamma) M I + (1 - \omega) \chi H, \\
		D_t	&=	\omega \psi H.
	\end{align}
